Circular Regression Trees and Forests with an\\\vspace{0.2em} Application to Probabilistic Wind Direction Forecasting

### 2020-03-23 pkg/circtree/inst/wind_paper/talks/ACINN_graduateseminar2020/slides/slides.Rnw
Include Achim's Input to slides (ACINN graduate seminar)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3001 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: a226746d60d62d3b29c747d0a714a10a4e5baa07

\textbf{Examples:} Circular data.
\begin{itemize}
\item Hourly crime data: $[0\text{h}, 24\text{h})$ with $0\text{h} = 24\text{h}$.
\item Directional behavior of animals: $[0^{\circ}, 360^{\circ})$ with $0^{\circ} = 360^{\circ}$.
\item Wind directions: $[0^{\circ}, 360^{\circ})$ with $0^{\circ} = 360^{\circ}$.
\end{itemize}

@@

%% SLIDE
\begin{frame}
\frametitle{Learning circular trees and forests}
      \begin{minipage}{0.7\textwidth}
      {\bf Forest:} 
      \begin{enumerate}
      \item Learn an ensemble of $T$ trees:\\
       Each tree is built on a bootstrap or subsample of the data, with
      random input variable sampling.
      \item<2-> Combine / average over estimated $T$ trees:\\
      To stabilize and regularize the model.
      \end{enumerate}
      \end{minipage}

>>>>

\textbf{Examples:} Circular data.
\begin{itemize}
\item Hourly crime data: $[0\text{h}, 24\text{h})$.
\item Directional behavior of animals: $[0^{\circ}, 360^{\circ})$.
\item Wind directions: $[0^{\circ}, 360^{\circ})$.
\end{itemize}

@@

%% SLIDE
\begin{frame}
\frametitle{Learning circular trees and forests}
      \begin{minipage}{1\textwidth}
      {\bf Forest:} 
      \begin{enumerate}
      \item Learn an ensemble of $T$ trees:\\
       Each tree is built on a bootstrap or subsample of the data, with
      random input variable sampling.
      \item<2-> Aggregate / average over estimated $T$ trees:\\
      To stabilize and regularize the model.
      %\item<3-> Only observations $\bold{x}_i$ in the same subgroup as a 
      %(new) observation $\bold{x}$ enter the parameter estimation.
      \item<2-> Weighted parameter estimation:\\The weight of observation $i$ for the parameter 
        estimatation for a 
        (new) observation $j$ is the mean of assignments to the same node.
      \end{enumerate}
      \end{minipage}
\begin{center}
\minipage{0.38\textwidth}
\vspace{0.5em}
\resizebox{0.94\textwidth}{!}{
\begin{tikzpicture}
  \visible<3->{
  \draw (11.1,5) node{\phantom{.}};
  \draw (18.5,9) node{\phantom{.}};

  \node[ellipse, fill=HighlightBlue!70, align=center] (n0) at (12, 9) {};
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1) at (11.5, 8) {\only<4->{$i, j$}};
  \draw[-, line width=1pt] (n0) -- (n1);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n2) at (12.5, 8) {};
  \draw[-, line width=1pt] (n0) -- (n2);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n3) at (12, 7) {};
  \draw[-, line width=1pt] (n2) -- (n3);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n4) at (13, 7) {};
  \draw[-, line width=1pt] (n2) -- (n4);
  }

  \visible<5->{

  \node[ellipse, fill=HighlightBlue!70, align=center] (n1_0) at (12+3.25, 9) {};
  \node[ellipse, fill=HighlightBlue!70, align=center] (n1_1) at (11.5+3.25, 8) {};
  \draw[-, line width=1pt] (n1_0) -- (n1_1);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1_2) at (12.5+3.25, 8) {\only<6->{$i, j$}};
  \draw[-, line width=1pt] (n1_0) -- (n1_2);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n1_3) at (11+3.25, 7) {};
  \draw[-, line width=1pt] (n1_1) -- (n1_3);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1_4) at (12+3.25, 7) {};
  \draw[-, line width=1pt] (n1_1) -- (n1_4);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1_5) at (10.5+3.25, 6) {};
  \draw[-, line width=1pt] (n1_3) -- (n1_5);
  \node[ellipse, fill=HighlightBlue!70, align=center] (n1_6) at (11.5+3.25, 6) {};
  \draw[-, line width=1pt] (n1_3) -- (n1_6);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1_7) at (11+3.25, 5) {};
  \draw[-, line width=1pt] (n1_6) -- (n1_7);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n1_8) at (12+3.25, 5) {};
  \draw[-, line width=1pt] (n1_6) -- (n1_8);

  \node[ellipse, fill=HighlightBlue!70, align=center] (n2_0) at (12+6, 9) {};
  \node[ellipse, fill=HighlightBlue!70, align=center] (n2_1) at (11.5+6, 8) {};
  \draw[-, line width=1pt] (n2_0) -- (n2_1);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n2_2) at (12.5+6, 8) {};
  \draw[-, line width=1pt] (n2_0) -- (n2_2);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n2_3) at (11+6, 7) {\only<6->{$i\vphantom{j}$}};
  \draw[-, line width=1pt] (n2_1) -- (n2_3);
  \node[rectangle, fill=HighlightOrange!70, align=center] (n2_4) at (12+6, 7) {\only<6->{$j$}};
  \draw[-, line width=1pt] (n2_1) -- (n2_4);
  }
\end{tikzpicture}
}
\endminipage
\end{center}
